Association between trauma severity models and opportunities for improvement:

### 2022-10-18 manuscript.Rmd
plots

The odds ratio for TRISS was `r t.stats[['or']]` (95% CI: `r t.stats[['or.ci']]`, p-value: `r t.stats[['or.p']]`). When plotting the ROC, the AUC was `r t.stats[['auc']]` (95% CI: `r t.stats[['auc.ci']][1]`-`r t.stats[['auc.ci']][3]`). The odds ratio for NORMIT was `r n.stats[['or']]` (95% CI: `r n.stats[['or.ci']]`, p-value: `r n.stats[['or.p']]`). When plotting the ROC, the AUC was `r n.stats[['auc']]` (95% CI: `r n.stats[['auc.ci']][1]`-`r n.stats[['auc.ci']][3]`).

>>>>

The odds ratio for TRISS was `r t.stats[['or']]` (95% CI: `r t.stats[['or.ci']]`, p-value: `r t.stats[['or.p']]`). When plotting the ROC, the AUC was `r t.stats[['auc']]` (95% CI: `r t.stats[['auc.ci']][1]`-`r t.stats[['auc.ci']][3]`). The integrated calibration index for TRISS was `r t.stats[['ici']]`.

The odds ratio for NORMIT was `r n.stats[['or']]` (95% CI: `r n.stats[['or.ci']]`, p-value: `r n.stats[['or.p']]`). When plotting the ROC, the AUC was `r n.stats[['auc']]` (95% CI: `r n.stats[['auc.ci']][1]`-`r n.stats[['auc.ci']][3]`). The integrated calibration index for NORMIT was `r n.stats[['ici']]`.

`r plot(t.perf, main="TRISS Receiver Operating Characteristic Curve", colorize = TRUE) `
`r plot(n.perf, main="NORMIT Receiver Operating Characteristic Curve", colorize = TRUE) `

`r plot(t.acc, main="TRISS Accuracy", colorize = TRUE) `
`r plot(n.acc, main="NORMIT Accuracy", colorize = TRUE) `
